Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-07-17 sections/3algebras.tex
Adding the changes discussed yesterday to section 3.2.

{\color{red} This is the statement in the absolute case, needs to be adapted to the relative case.}

\begin{lemma}\label{lem:gluing_disk/M}
    A Weiss sieve $\mathscr{U} \subset \mfld[r]_{/M}$ canonically determines a morphism
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \mathsf{RFib}_{\disk(\bstr)}) \xrightarrow{\ \ \simeq \ \ } \disk_{/M}
    \end{equation}
    of right fibrations over $\disk(\bstr)$, which moreover, is an equivalence.
\end{lemma}

\begin{proof}
    The morphism is determined by the universal property of the colimit with the component maps $\disk_{/U} \xrightarrow{} \disk_{/M}$ given from the open embeddings $U \xhookrightarrow{} M$. To show the equivalence, we follow a related strategy to the one laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}. By \cite[Def.2.2.3.2]{lurie_htt}, a morphism of right fibrations, as in the statement, is an equivalence if, and only if, it induces equivalences of spaces on the fibers over each object of the base. The objects of the base $\disk(\bstr)$ (e.g. according to \cite[Lem.2.21]{aft_fhstrat}) are lists $(i_{[U]} | [U] \in [\bstr])$ of integers, one for each isomorphism class of objects in $\bstr$\footnote{The choice of $\bstr$-structure does not play much of a role, because if we don't choose the appropriate one some fibers can be trivial, but this does not impede the result.}. According to the same lemma, the fibers are given by the spaces
    %
    \begin{equation}
        (\disk_{/M})_{(i_{[U]} | [U])} \simeq \coprod_{[U]} \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}.
    \end{equation}
    %
    Thus, we endeavor to show that the induced morphism
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-_{[U]})_{\Sigma_{i_{[U]}}}} \mathsf{Sp}) \xrightarrow{\ \ \ \ \ } \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}
    \end{equation}
    %
    is an equivalence of spaces for all isomorphism classes of basics $[U]$ and for all $i_{[U]} \geq 0$. From a Weiss sieve $\mathscr{U}$ of $M$ we easily get a Weiss sieve $\mathscr{U}_{[U]}$ of $M_{[U]}$ by intersecting with $M_{[U]}$ as a submanifold of $M$. Using $\mathscr{U}_{[U]}$, we define $\mathscr{U}_{i_{[U]}, [U]}$ to be the sieve of $\mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}$ as in \Cref{lem:weiss_to_ordinary}. These considerations give us equivalences
    %
    \begin{align}\label{eq:ord_to_W_equivs}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-_{[U]})_{\Sigma_{i_{[U]}}}} \mathsf{Sp}) &\simeq \mathsf{colim} (\mathscr{U}_{[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{\mathrm{Conf}_{i_{[U]}}(-)_{\Sigma_{i_{[U]}}}} \mathsf{Sp})\notag\\
        &\simeq \mathsf{colim} (\mathscr{U}_{i_{[U]},[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}).
    \end{align}
    %
    The second equivalence in the above is simply a statement about the unions over the two covers and is a restatement of \Cref{lem:weiss_to_ordinary}. But, by \cite[Prop.A.3.2]{lurie_ha} the induced map is an equivalence
    %
    \begin{equation}\label{eq:gluing_top_lurie}
        \mathsf{colim} (\mathscr{U}_{i_{[U]},[U]} \xrightarrow{} \mfld[r](\bstr) \xrightarrow{} \mathsf{Sp}) \xrightarrow{\ \ \simeq \ \ } \mathrm{Conf}_{i_{[U]}}(M_{[U]})_{\Sigma_{i_{[U]}}}.
    \end{equation}
\end{proof}

\begin{lemma}\label{lem:gluing_disk/M/e}
    A Weiss sieve $\mathscr{U} \subset \mfld[r]_{/M}$ canonically determines a morphism
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{(\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \xrightarrow{\ \ \simeq \ \ } (\disk_{/M})_{/-}
    \end{equation}
    of right fibrations over $\disk_{/M}$, which moreover, is an equivalence.
\end{lemma}

\begin{proof}
    .....
\end{proof}

@@

\begin{proof}
    First consider the special case when $(\iota: \mathscr{D} \xrightarrow{} \mathscr{M}) = (y_{\mathscr{D}}: \mathscr{D} \xrightarrow{} \mathsf{PShv}(\mathscr{D}))$ the Yoneda embedding of $\mathscr{D}$. We will see that in this case, $L_{y_{\mathscr{D}}} F$ is colimit preserving because it is a left adjoint to the functor
    %
    \begin{equation}
        T_F: \catC \xrightarrow{y_{\catC}} \mathsf{PShv} (\catC) \xrightarrow{F^*} \mathsf{PShv} (\mathscr{D}).
    \end{equation}
    %
    %Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there is an equivalence of morphism spaces $\mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) \simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F (c))$ given by 
    %
    %\begin{align}
    %    \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\simeq \mathsf{Hom}_{\catC} (F (d), c) \simeq \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \simeq \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
    %\end{align}
    %
    %In general, the Yoneda embedding $y_{\mathscr{D}}$ is a dense functor

@@

    With the Weiss cosheaf property being a statement about preserving colimits, and with $\int F$ being a left Kan extension we are exactly in the situation of \Cref{lem:Lan_preserve_colim}. Thus, we only need to show that functor $T: \mfld_{/M} \xrightarrow{} \mathsf{PShv} (\disk_{/M})$\footnote{This functor is related to the tangent classifier, with the differences being that we're now in the relative case, and we're not fully limiting to $\bsc$ but instead only to disks.} preserves Weiss colimits, namely that there is an equivalence
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{T} \mathsf{PShv} (\disk_{/M})) \simeq T(N \xhookrightarrow{} M),
    \end{equation}
    %
    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve. If we also append the straightening--unstraightening construction to $T$, we can write the desired equivalence as
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{ (\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \simeq (\disk_{/M})_{/e}.
    \end{equation}
    %
    \Cref{lem:gluing_disk/M/e} guarantees the existence of this equivalence.
\end{proof}

@@

The above proof already shows how the ideas that went into defining factorization algebras are not that different from the ideas that went into defining factorization homology. Namely, the ideas of Weiss cosheaves and algebras over disks are deeply connected. Now that this connection has been explained, the proof of \Cref{thm:disk_alg=lcfa}, which we delve into promptly, is not hard to establish.

\begin{proof}[Proof of {\Cref{thm:disk_alg=lcfa}}]
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding an equivalence of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure (see \Cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    where $F|$ is the restriction of $F$ to disks, and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) \simeq \int_U F|.
    \end{equation}
    %
    Naturality of these equivalences is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. Given this fact, to preserve the multiplicative structure it is enough to show that the following is a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. This, however, is guaranteed by the equivalences
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}

    To show full faithfulness we need to find equivalences of morphism spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\lcfa_M (\catC)} (\int A, \int B),
    \end{equation}
    %
    for each $A, B \in \alg{\disk_{/M}}$. However, since the functors
    %
    \begin{align}
        &\alg{\disk_{/M}} (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\disk[r]_{/M}} (\catC) &\lcfa_M (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\mfld[r]_{/M}} (\catC)
    \end{align}
    %
    are both fully faithful we are reduced to finding equivalences
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk[r]_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\alg{\mfld[r]_{/M}} (\catC)} (\int A, \int B).
    \end{equation}
    %
    The existence of these is exactly the requirement that factorization homology in the usual sense is fully faithful, which is part of the statement of \cite[lem.2.17]{aft_fhstrat}
\end{proof}

>>>>

%To show the equivalence, we follow a related strategy to the one laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}.

\begin{lemma}\label{lem:gluing_disk/M/e}
    A Weiss sieve $\mathscr{U} \subset (\mfld[r]_{/M})_{/e}$ canonically determines a morphism
    %
    \begin{equation}
        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\cdot, -)} \mathsf{PShv}(\disk_{/M}) \big) \xrightarrow{\ \ \simeq \ \ } \mathsf{Hom}_{\mfld_{/M}}(\cdot, e)
    \end{equation}
    of presheaves over $\disk_{/M}$, which moreover, is an equivalence.
\end{lemma}

\begin{proof}
    The morphism is determined by the universal property of the colimit. The components of the morphism of presheaves are given by
    %
    \begin{equation}
        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\iota, -)} \mathsf{Sp} \big) \xrightarrow{\ \ \ \ \ } \mathsf{Hom}_{\mfld_{/M}}(\iota, e),
    \end{equation}
    %
    for each $\iota \in \disk_{/M}$, an open embedding of disks in $M$, and these morphisms are now maps of spaces which we want to show are equivalences. We now study the hom-spaces appearing above. By definition of the slice $\infty$-category, the hom-spaces are given as the homotopy fibers
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\mfld_{/M}} (\iota, e) \arrow[d] \arrow[r] & \mathsf{Hom}_{\mfld}(D, N) \arrow[d, "e^*"] \\
            * \arrow[r, "\{\iota\}"] & \mathsf{Hom}_{\mfld}(D, M),
        \end{tikzcd}
    \end{equation}
    %
    where we have fixed the notation $\iota: D \xhookrightarrow{} M$ and $e: N \xhookrightarrow{} M$, for the domains of these maps. We further establish the notation that for each isomorphism class of basics $[B]$, the fixed $D$ has $i_[B]$-many disks of type $[B]$. With this notation in hand, by the characterization of the maximal $\infty$-subgroupoid of $\disk_{/M}$ \cite[Lem.2.21]{aft_fhstrat} for example, we know that
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld}(D, M) \simeq \coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(M_{[B]}),
    \end{equation}
    %
    where the notation $M_{[B]}$ denotes the $[B]$-stratum of $M$ (see \cite[Prop.4.4.7]{aft_localstrut}). We also note that under these equivalences the map $e^*$ is given by $\coprod_{[B]} \mathrm{UConf}_{i_{[B]}}(e_{[B]})$, which is even an open inclusion. Thus, the hom-spaces of the slice $\infty$-category are given as 
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld_{/M}} (\iota, e) \simeq \coprod_{[B]} \mathsf{Fib}_\iota^{[B]}(e),
    \end{equation}
    %
    where $\mathsf{Fib}_\iota^{[B]}(e)$ is defined as the homotopy fiber
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Fib}_\iota^{[B]}(e) \arrow[d] \arrow[r] & \mathrm{UConf}_{i_{[B]}}(N_{[B]}) \arrow[d, "\mathrm{UConf}_{i_{[B]}}(e_{[B]})"] \\
            * \arrow[r, "\{\iota_{[B]}\}"] & \mathrm{UConf}_{i_{[B]}}(M_{[B]}),
        \end{tikzcd}
    \end{equation}
    %
    where, by slight abuse, we denoted the point over which the fiber lies with $\iota_{[B]}$ as well. With all of this notation in place, and by switching the places of the colimits, what we want to show is that the canonical maps
    %
    \begin{equation}
        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Fib}_{\iota}^{[B]}(-)} \mathsf{Sp} \big) \xrightarrow{\ \ \ \ \ } \mathsf{Fib}_{\iota}^{[B]}(e),
    \end{equation}
    %
    are equivalences for every $\iota$ and every $[B]$. Using \cite[Prop.A.3.2]{lurie_ha}, a sufficient condition for these maps to be equivalences is for the composition $\mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Fib}_{\iota}^{[B]}(-)} \mathsf{Sp}$ to be a covering sieve of $\mathsf{Fib}_{\iota}^{[B]}(e)$. To exhibit such a property we pick a particular model for the homotopy fiber $\mathsf{Fib}_{\iota}^{[B]}(e)$, namely
    %
    \begin{equation}
        \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N) := \big( \mathsf{P}(\mathrm{UConf}_{i_{[B]}}(M_{[B]})) \times \mathrm{UConf}_{i_{[B]}}(N_{[B]}) \big) / (s (p) = \iota_{[B]}, t (p) = e(x)),
    \end{equation}
    %
    the space of paths in $\mathrm{UConf}_{i_{[B]}}(M_{[B]})$ that start at $\iota_{[B]}$ and end at a point $x$ in $\mathrm{UConf}_{i_{[B]}}(N_{[B]})$. With this model, for each $(U \xhookrightarrow{} N) \in \mathscr{U} \subset (\mfld[r]_{/M})_{/e} \simeq \mfld[r]_{/N}$ (by \Cref{lem:double_slice}) we get an open inclusion
    %
    \begin{equation}
        \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U) \xhookrightarrow{\ \ \ \ } \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N),
    \end{equation}
    %
    and we're trying to show that the collection $\mathscr{V}_{\iota}^{[B]}$ of these is a cover.

    Given a Weiss cover $\mathscr{U}$ on $N$ we can restrict it to a Weiss cover $\mathscr{U}_{[B]}$ of $N_{[B]}$ by intersecting. The statement of \Cref{lem:weiss_to_ordinary} is that we can build an ordinary cover $\mathscr{U}_{i_{[B]},[B]}$ of $\mathrm{UConf}_{i_{[B]}}(N_{[B]})$. $\mathscr{V}_{\iota}^{[B]}$ is a cover if for any $p \in \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N)$ we can find an open $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ that contains it. But this is indeed the case, because looking at the target $t(p)$ of the path $p$, we get $t(p) \in \mathrm{UConf}_{i_{[B]}}(N_{[B]})$, and we know that there exists a $U \in \mathscr{U}$ such that $\mathrm{UConf}_{i_{[B]}}(U_{[B]})$ covers $t(p)$ and subsequently also that $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ covers $p$.

    ...
\end{proof}

@@

\begin{proof}
    First consider the special case when $(\iota: \mathscr{D} \xrightarrow{} \mathscr{M}) = (y_{\mathscr{D}}: \mathscr{D} \xrightarrow{} \mathsf{PShv}(\mathscr{D}))$ the Yoneda embedding of $\mathscr{D}$. We will see that in this case, $L_{y_{\mathscr{D}}} F$ is colimit preserving because it is a left adjoint to the functor
    %
    \begin{equation}
        T_F: \catC \xrightarrow{y_{\catC}} \mathsf{PShv} (\catC) \xrightarrow{F^*} \mathsf{PShv} (\mathscr{D}).
    \end{equation}
    %
    Indeed, let $X \simeq y_{\mathscr{D}} (d)$ be a representable presheaf, then there are maps of morphism spaces
    %
    \begin{align}
        \mathsf{Hom}_{\catC} (L_{y_{\mathscr{D}}} F (X), c) &\xrightarrow[\simeq]{} \mathsf{Hom}_{\catC} (F (d), c) \xrightarrow[\simeq]{y_{\mathscr{C}}} \mathsf{Hom}_{\mathsf{PShv}(\catC)} (y_{\catC}(F(d)), y_{\catC}(c))\notag\\ &\xrightarrow{F^*} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (F^*(y_{\catC}(F(d))), T_F(c)) \xrightarrow[\simeq]{} \mathsf{Hom}_{\mathsf{PShv}(\mathscr{D})} (X, T_F(c)).
    \end{align}
    %
    The Yoneda embedding $y_{\mathscr{D}}$ is a dense functor, so the above argument holds

@@

    With the Weiss cosheaf property being a statement about preserving colimits, and with $\int F$ being a left Kan extension we are exactly in the situation of \Cref{lem:Lan_preserve_colim}. Thus, we only need to show that the functor $T: \mfld_{/M} \xrightarrow{} \mathsf{PShv} (\disk_{/M})$ preserves Weiss colimits. Namely, we need to show that there is an equivalence
    %
    \begin{equation}
        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\cdot, -)} \mathsf{PShv} (\disk_{/M}) \big) \xrightarrow{\ \ \simeq \ \ } \mathsf{Hom}_{\mfld_{/M}}(\cdot, e),
    \end{equation}
    %
    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.\footnote{If we also append the straightening--unstraightening construction to $T$, the desired equivalence can equivalently be written as
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{ (\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \simeq (\disk_{/M})_{/e}.
    \end{equation}}
    %
    But this is exactly the result of \Cref{lem:gluing_disk/M/e}.
\end{proof}

@@

The above proof also shows how the ideas that went into defining factorization algebras are not that different from the ideas that went into defining factorization homology. Namely, the ideas of Weiss cosheaves and algebras over disks are deeply connected. Now that this connection has been explained, the proof of \Cref{thm:disk_alg=lcfa}, which we delve into promptly, is not hard to establish.

\begin{proof}[Proof of {\Cref{thm:disk_alg=lcfa}}]
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding an equivalence of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure (see \Cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    where $F|$ is the restriction of $F$ to disks, and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) \simeq \int_U F|.
    \end{equation}
    %
    Naturality of these equivalences is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. Given this fact, to preserve the multiplicative structure it is enough to show that the following is a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. This, however, is guaranteed by the equivalences
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}
    %
    Indeed, the fact that (sifted) colimits commute with the monoidal product on $\catC$ means that, for example in the case of two objects
    %
    \begin{align}
        \mathsf{colim}(K \xrightarrow{F} \catC) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC) &\simeq \mathsf{colim}(K \xrightarrow{F(-) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC)} \catC)\notag\\
        &\simeq \mathsf{colim}(K \xrightarrow{\mathsf{colim}(K' \xrightarrow{F(-) \otimes F'(-)} \catC)} \catC)\notag\\
        &\simeq \mathsf{colim}(K \times K' \xrightarrow{F \times F'} \catC \times \catC \xrightarrow{- \otimes -} \catC),
    \end{align}
    %
    for any (sifted) indexing $\infty$-categories $K, K'$.

    To show full faithfulness we need to find equivalences of morphism spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\lcfa_M (\catC)} (\int A, \int B),
    \end{equation}
    %
    for each $A, B \in \alg{\disk_{/M}}$. However, since the functors
    %
    \begin{align}
        &\alg{\disk_{/M}} (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\disk[r]_{/M}} (\catC) &\lcfa_M (\catC) \xrightarrow{\mathsf{f.f.}} \alg{\mfld[r]_{/M}} (\catC)
    \end{align}
    %
    are both fully faithful we are reduced to finding equivalences
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk[r]_{/M}} (\catC)} (A, B) \simeq \mathsf{Hom}_{\alg{\mfld[r]_{/M}} (\catC)} (\int A, \int B).
    \end{equation}
    %
    The existence of these is exactly the requirement that factorization homology in the usual sense is fully faithful, which is part of the statement of \cite[lem.2.17]{aft_fhstrat}.
\end{proof}
